Output Summary

### 2021-12-07 03-post-process/output-plots.Rmd
Add Bayesian p-value calculations for winter tagging data

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "new-BH"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

# which years are "observable" for at least some quantities?
observable = 2:jags_data$ny_obs

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Egg-to-Parr Survival"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Realized Survival", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_Lphi_f_Pb", "rho_Lphi_f_Pb", "^phi_f_Pb[", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# parr survival from summer to winter tagging
L1 = "Survival From Summer to Winter"
match = c("phi_Pb_Pa[2,.]")
phi_Pb_Pa_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1)))

@@

# Initial adult recruitment
L1 = "Initial Adult Returns"
L2 = c("Age-3", "Age-4", "Age-5")
match = c("Rb\\[[2|3|4],1,1,.\\]", "Rb\\[[2|3|4|5],2,1,.\\]", "Rb\\[[2|3|4|5|6],3,1,.\\]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[[i]], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

```{r make-mean-zero-resid-table}
# extract posterior mean residual time series for each population
resids = lapply(1:4, get_resids, post = diag_post)

@@

### Winter Parr $\rightarrow$ LGR

```{r winter-surv-fit, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]$", year = observable, LH_type = i_spring, pop = j)),
               get_obs_ests_logit_normal(jags_data$Lphi_obs_Pa_Ma[observable,i_spring,j], jags_data$sig_Lphi_obs_Pa_Ma[observable,i_spring,j]),
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, TeX("$Winter\\,Parr \\rightarrow LGR\\,Survival$"))
```

@@

# Migratory Strategy Apportionment

```{r pi-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^pi[year,LH_type,pop]$", year = ts_yrs, LH_type = i_fall, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Proportion of Parr with Fall Migration Strategy")
```

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_Lphi_f_Pb[.]$", "Process SD")
my_boxplot("^rho_Lphi_f_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny_obs

@@

```{r calculate-mcmc-diagnostics}
# parr recruitment
L1 = "Parr Recruitment"
L2 = c("BH Productivity", "BH Capacity", "Capacity vs. Habitat Slope", "Capacity vs. slope SD", "Process SD", "Among-pop Correlation", "Parr States")
match = c("alpha", "^beta[", "mu_beta_per_wul", "sig_lbeta", "sig_lPb", "rho_lPb", "^Pb[")
parr_recruit_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

@@

# Initial adult recruitment
L1 = "Initial Adult Recruitment"
L2 = c("Mean", "Realized")
match = c("mu_init_recruits[.]", "^init_recruits[.+,.]")
init_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

```{r make-mean-zero-resid-table}
# extract posterior mean residual time series for each population
resids = lapply(1:4, get_resids, post = post)

@@

@@

@@

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_lPb[.]$", "Process SD")
my_boxplot("^rho_lPb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```
